Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems

### 2024-06-15 final/oup-authoring-template.tex
Update captions reflecting order changes in figures

  \subcaption{\label{fig-first-order}First-order system of an exponential decay. The variable
  \texttt{x} stores the initial condition for \(x\), and the variable
  \texttt{eq} stores the rate equation for \(x\).}
  \end{minipage}%
  \newline
  \begin{minipage}[t]{\columnwidth}

@@

  \subcaption{\label{fig-composition}First-order system of two exponential decays by composition of
  the \texttt{Decay} system. The subsystem \texttt{linked} has a reference
  to the outer variable \texttt{x}, while the subsystem
  \texttt{independent} defines a new variable with initial condition $2$,
  which on the corresponding mathematical expression was named \(x_{ind}\).}
  \end{minipage}%

  \caption{\label{fig-poincare}Code and corresponding mathematical
  expressions for different systems.}

@@

% FIGURE 2
\begin{figure}[t]
  \includegraphics[width=\columnwidth]{ide1.pdf}
  \includegraphics[width=\columnwidth]{ide2.pdf}
  \caption{
    \label{fig-ide}
    Screenshots of Visual Studio Code showing
    tooltips (green arrows) and
    highlighted type errors (red arrows).
    On the left,
    we show that \texttt{a},
    a \texttt{Constant} assigned with \texttt{assign(...,\ constant=True)},
    can be used for \texttt{Variable b}'s initial condition.
    Instead,
    it is flagged as a type error (red underlining)
    when using \texttt{c}, a \texttt{Parameter},
    for \texttt{Variable d}'s initial condition,
    The IDE automatically recognizes \texttt{e} as an \texttt{Equation},
    and provides autocompletion of the \texttt{Model}'s components.
    A tooltip is shown when composing models (green arrow, right),
    which show the expected variables and their default values.
    The IDE highlights wrong names (\texttt{z} is not a name in \texttt{Model})
    and mismatched types (\texttt{x} is \texttt{Variable} and \texttt{a} must be a number or a \texttt{Constant})
  }  
\end{figure}

@@

\CommentTok{\# from existing SBML file}
\VariableTok{model} \OperatorTok{=} \ClassTok{sbml}.\FunctionTok{load}\KeywordTok{(}\StringTok{"repressilator.sbml"}\KeywordTok{)}
\CommentTok{\# from BioModels}
\VariableTok{model} \OperatorTok{=} \ClassTok{biomodels}.\FunctionTok{load}\KeywordTok{(}\StringTok{"BIOMD12"}\KeywordTok{)}
\VariableTok{model}
\end{Highlighting}
  \end{CodeInput}

@@

  \caption{Creation of a model from a local SBML file or one uploaded to BioModels.}
  \label{fig-simbio-io}
\end{figure}

>>>>

  \subcaption{
    \label{fig-first-order}
    First-order system of an exponential decay.
    The variable \texttt{x} stores the initial condition for \(x\),
    and the variable \texttt{eq} stores its rate equation.
  }
  \end{minipage}%
  \newline
  \begin{minipage}[t]{\columnwidth}

@@

  \subcaption{
    \label{fig-composition}
    First-order system of two exponential decays by composition of the \texttt{Decay} system.
    The subsystem \texttt{linked} has a reference to the outer variable \texttt{x},
    while the subsystem \texttt{independent} defines a new variable with initial condition $2$,
    which on the corresponding mathematical expression was named \(x_{indep}\).
  }
  \end{minipage}%

  \caption{
    \label{fig-poincare}
    Code and corresponding mathematical expressions for different systems.
  }

@@

% FIGURE 2
\begin{figure}[t]
  \includegraphics[width=\columnwidth]{ide1.pdf}
  \includegraphics[width=\columnwidth]{ide2.pdf}
  \caption{
    \label{fig-ide}
    Screenshots of Visual Studio Code showing
    tooltips (green arrows) and
    highlighted type errors (red arrows).
    Above,
    we show that \texttt{a},
    a \texttt{Constant} assigned with \texttt{assign(...,\ constant=True)},
    can be used for \texttt{Variable b}'s initial condition.
    Instead,
    it is flagged as a type error (red underlining)
    when using \texttt{c}, a \texttt{Parameter},
    for \texttt{Variable d}'s initial condition,
    The IDE automatically recognizes \texttt{e} as an \texttt{Equation},
    and provides autocompletion of the \texttt{Model}'s components.
    A tooltip is shown when composing models (green arrow, below),
    which show the expected variables and their default values.
    The IDE highlights wrong names (\texttt{z} is not a name in \texttt{Model})
    and mismatched types (\texttt{x} is \texttt{Variable} and \texttt{a} must be a number or a \texttt{Constant})
  }  
\end{figure}

@@

\CommentTok{\# from a local SBML file}
\VariableTok{model} \OperatorTok{=} \ClassTok{sbml}.\FunctionTok{load}\KeywordTok{(}\StringTok{"repressilator.sbml"}\KeywordTok{)}
\CommentTok{\# from BioModels}
\VariableTok{model} \OperatorTok{=} \ClassTok{biomodels}.\FunctionTok{load}\KeywordTok{(}\StringTok{"BIOMD12"}\KeywordTok{)}
\VariableTok{model}
\end{Highlighting}
  \end{CodeInput}

@@

  \caption{Creation of a model from a local SBML file or from one uploaded to BioModels.}
  \label{fig-simbio-io}
\end{figure}
